BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-11-28 tex/0-abstract.tex
Add missing files, update abstract.

Blogs are by nature a very dynamic and volatile communication medium. The BlogForever project aims on providing a generic platform for blog preservation, thus ensuring access to this information for future generations. This paper presents a key component of this archiving system: the web crawler. More precisely, our discussion will concentrate on techniques to automatically extract content, authors, dates and comments from blog posts. One of the main challenges in the preservation of web objects is the rapid evolution of technologies. For instance, the recent trend towards using JavaScript to dynamically generate pages on the client side constitutes a new obstacle for today's crawlers. We will show how we integrated a web browser into the harvesting process in order to address this issue. Furthermore, we will present a simple and robust algorithm based on string matching between web feeds and page content to generate wrappers. Being applicable to all posts of a blog, the resulting extraction process scales to blogs with large amounts of posts.
\comment{"being applicable to all posts of a blog" --> sounds a bit weird.}

>>>>

Blogs are by nature a very dynamic and volatile communication medium. The BlogForever project aims on providing a generic platform for blog preservation, thus ensuring access to this information for future generations. This paper presents a key component of this archiving system: the web crawler. More precisely, our discussion will concentrate on techniques to automatically extract content, authors, dates and comments from blog posts. One of the main challenges in the preservation of web objects is the rapid evolution of technologies. For instance, the recent trend towards using JavaScript to dynamically generate pages on the client side constitutes a new obstacle for today's crawlers. We will show how we integrated a web browser into the harvesting process in order to address this issue. Furthermore, we will present a simple and robust algorithm to generate extraction rules based on string matching between a web feed and blog page contents. Our crawler will then use these rules throughout the blog, leading to a scalable extraction process.
